How Slow do my Transient Type Checks Go?

### 2019-08-17 paper.tex
Fixed english

To identify type annotations causing anomalies,
% To investigate Moth's support for transient type checks further, 
we adapted the Takikawa protocol
and take inspiration from the Takikawa-Vitousek variant.
For each benchmark, we generated 100 partially typed versions,
or fewer if the benchmark has less than 11 types.
We did an even split so that for each interval $i \ge 1$ and $i$ < $N$, we generated roughly the same number of configurations with $i$ type annotations. We used Robert Floyd's sampling algorithm \cite{Bentley:1987:PPS:30401.315746} to choose the type annotations each configuration contained randomly, and we ensured that no duplicate configurations were generated. In addition to these, we tested fully untyped and typed versions, for a total of 102 configurations per benchmark (or 97 in the case of our Storage benchmark, since it only has 10 type annotations).

@@

Before we start to investigate specific type annotations,
we present the performance measurements of our sample of the typing lattice configurations in figure~\ref{f:full}.
These results are the foundation for a more details analysis.

>>>>

To identify type annotations causing anomalies,
% To investigate Moth's support for transient type checks further, 
we adapted the Takikawa protocol
and took inspiration from the Takikawa-Vitousek variant.
For each benchmark, we generated 100 partially typed versions,
or fewer if the benchmark has less than 11 types.
We did an even split so that for each interval $i \ge 1$ and $i$ < $N$, we generated roughly the same number of configurations with $i$ type annotations. We used Robert Floyd's sampling algorithm \cite{Bentley:1987:PPS:30401.315746} to choose the type annotations each configuration contained randomly, and we ensured that no duplicate configurations were generated. In addition to these, we tested fully untyped and typed versions, for a total of 102 configurations per benchmark (or 97 in the case of our Storage benchmark, since it only has 10 type annotations).

@@

Before we start to investigate specific type annotations,
we present the performance measurements of our sample of the typing lattice configurations in figure~\ref{f:full}.
These results are the foundation for a more detailed analysis.
